Reply To Examiners

### 2014-04-24 answer_thesis_examiner/old.chap2.tex
auto commit

( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
Unfortunately I do not have it at hand.
It would be great if I can have a look at it!)

The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
I really appreciate the examiner effort in pointing out specific references.
They, and some other articles, have been included in the thesis.
I would like however to seek his empathy towards a couple of points.
First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
While they do results in published scientific articles, 
  they are not, however, to be considered as the main contributions of the thesis.
Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.

>>>>

%( \textbf{ Hai note: }  The Examiner mentions further clarifications to support the claim of novelty in Part II of his report.
%Unfortunately I do not have it at hand.
%It would be great if I can have a look at it!)

The Examiner also suggestion the inclusion of several particular references into \textbf{the literature review}.
I really appreciate the examiner effort in pointing out specific references \cite{Argenti_GRSM_2013, Lee_RSReviews_1994, Cetin_ProcSPIE_2000, White_ProcSPIE_1994, Sattar_TIP_1997, Wang_TIP_2004, Nielsen_2012_ICASSP}.
They, and some other articles, have been included in the thesis.

%The examiner also suggestion inclusion of several references into \textbf{the literature review} topics of ``relevant SAR/POLSAR speckle filters'' and  ``evaluation of SAR speckle filters''.
%I really appreciate the examiner effort in pointing out specific references.
%They, and some other articles, have been included in the thesis.
%I would like however to seek his empathy towards a couple of points.
%First, a number of the references cited has already been included into the original thesis (e.g \cite{Touzi_2002_TGRS} or \cite{Xie_2002_TGRS}.). 
%Some of them (for example \cite{Argenti_GRSM_2013}) are actually published (Sept 2013) after the submission of the original thesis (Aug 2013).
%Second, please also note that the topics of SAR/POLSAR speckle filters and to some extend, their evaluation, may be considered as part of the thesis's contribution.
%While they do results in published scientific articles, 
%  they are not, however, to be considered as the main contributions of the thesis.
%Rather they serves as application, or demonstration, of the benefits of the thesis's main proposal.
%As such, while I understand the need for comprehensive review, due to various constraint, I seek his understanding that they are probably not to be explored with the same depth and coverage as the main topic of the thesis.
